Annotated example of index standardization with VAST

### 2021-11-24 doc/appendix-pcod-VAST.Rmd
Minor VAST tweaks

```{r, echo = TRUE}
FieldConfig <- matrix(c("IID", "IID", "IID", "IID", "IID", "IID"),
  ncol = 2, nrow = 3,
  dimnames = list(
    c("Omega", "Epsilon", "Beta"),
    c("Component_1", "Component_2")
  )
)
RhoConfig <- c("Beta1" = 0, "Beta2" = 0, "Epsilon1" = 0, "Epsilon2" = 0)
```

@@

>>>>

```{r config, echo = TRUE}
FieldConfig <- matrix(c("IID", "IID", "IID", "IID", "IID", "IID"),
  ncol = 2, nrow = 3,
  dimnames = list(
    c("Omega", "Epsilon", "Beta"),
    c("Component_1", "Component_2")
  )
)
FieldConfig
RhoConfig <- c("Beta1" = 0, "Beta2" = 0, "Epsilon1" = 0, "Epsilon2" = 0)
```

@@

This document was built using:

```{r, echo=TRUE}
R.Version()$version.string
packageVersion("VAST")
packageVersion("FishStatsUtils")
```
